Modeling tabular icebergs coupled to an ocean model

### 2017-02-08 Icebergs_only.tex
Editing iceberg only version

The goal of this study is to develop a new iceberg model where tabular icebergs are explicitly resolved in the ocean. In this model, icebergs are no longer treated as point particles that feel the ocean at one point, but rather the icebergs have structure, depress the ocean surface, and can feel the ocean across multiple ocean grid cells. To do this, we create tabular icebergs out of many Lagrangian elements which are `bonded' together by numerical bonds. The numerical bonds hold the ice elements together and allow a collection elements to move as a unit. By manually breaking these bonds, we can simulate iceberg calving, allowing us to study the ocean response to giant iceberg detaching from an ice shelf or the fracturing of a large iceberg into smaller pieces.

The discrete element model (DEM) developed in this study is referred to at the Lagrangian Tabular Iceberg Model (LTAM). Section 2 gives a description of many of the key aspects of the LTAM. Since this model is a new approach to modeling iceberg, we present many of the technical elements involved in constructing the model. In Section 3 and 4, we demonstrate the capabilities of the model by simulating a tabular iceberg detaching from an idealized ice shelf.

@@

 \section{Summary}
In study above we have presented a novel method that can be used to representing tabular icebergs in numerical ocean models. In this framework, tabular icebergs (or ice shelves) are constructed out of Lagrangian particles which are held together by numerical bonds. In this way icebergs are not treated as point particles (as in previous iceberg models), but rather are explicitly resolved in the ocean. This allows the icebergs to apply pressure to the ocean surface over a wide area (larger than a grid cell), and affect circulation patterns in a way that is more physically realistic.

>>>>

The goal of this study is to develop a new iceberg model where tabular icebergs are explicitly resolved in the ocean. In this model, icebergs are no longer treated as point particles that feel the ocean at one point, but rather the icebergs have structure, depress the ocean surface, and can feel the ocean across multiple ocean grid cells. To do this, we create tabular icebergs out of many Lagrangian elements which are `bonded' together by numerical bonds. The numerical bonds hold the ice elements together and allow a collection elements to move as a unit. By manually breaking these bonds, we can simulate iceberg calving, allowing us to study the ocean response to giant iceberg detaching from an ice shelf (e.g.: Figure \ref{fig:Spread_area} and \ref{fig:SST_Collapse}) or the fracturing of a large iceberg into smaller pieces.

The discrete element model (DEM) developed in this study is referred to at the Lagrangian Tabular Iceberg Model (LTAM). 
%The LTAM model is coupled to the MOM6 numerical ocean model \citep{Hallberg2013}. 
Section 2 gives a description of many of the key aspects of the LTAM. Since this model is a new approach to modeling iceberg, we present many of the technical elements involved in constructing the model. In Section 3 and 4, we demonstrate the capabilities of the model by simulating a tabular iceberg detaching from an idealized ice shelf.

@@

 \section{Summary}
In study above we have presented a novel method that can be used to represent tabular icebergs in numerical ocean models. In this framework, tabular icebergs (or ice shelves) are constructed out of Lagrangian particles which are held together by numerical bonds. In this way icebergs are not treated as point particles (as in previous iceberg models), but rather are explicitly resolved in the ocean. This allows the icebergs to apply pressure to the ocean surface over a wide area (larger than a grid cell), and affect circulation patterns in a way that is more physically realistic.
